### 2023-03-19 Conference Submission/DraftDoc.tex
Maybe sorting stuff out

\begin{section}{Results and Discussion}
    For each of theses systems, we took embedded the temporal network in two dimensions at each time step. The temporal embeddings were then divided into a training set of 20 and a testing set of 15. The output of the trained neural networks was then used to train a symbolic regression model that could use a simple set of addition, subtraction, division, and multiplication. \\
    In fig \autoref{2community series}, \autoref{longtail series},\autoref{3community series} the green points are the embedded coordinates of the node in each of the communities. Each cluster is one separate community. The orange point is the true coordinate of the embedded target node at each time step. The blue point is our model prediction from the true target node at the first time step. As the time progresses, we see the true node move from one community cluster to the other. This is expected from the embedding; the target node starts as very similar to the first community (as it has many connections with nodes in that community) and as time progresses, it gradually becomes less and less similar to the first community and more similar to the second (as the edges between the target node and the first community are replaced with edges to the second community). As such, we see the target node move towards the second community.
    \begin{subsection}{2 Community}
        \begin{figure}
            \foreach \i in {1,...,15} {%
                \begin{subfigure}[p]{0.3\textwidth}
                    \includegraphics[width=\linewidth]{/home/stirling/thesis/Conference Submission/Plots/Test Only/2communities/2communities \i.png}
                    \caption{t=\i}
                \end{subfigure}\quad
            }
            \caption{2 Community test series. This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the two community system.}
            \label{2community series}
        \end{figure}

@@

    \begin{subsection}{Long Tail}
        \begin{figure}
            \foreach \i in {1,...,15} {%
                \begin{subfigure}[p]{0.3\textwidth}
                    \includegraphics[width=\linewidth]{/home/stirling/thesis/Conference Submission/Plots/Test Only/longTail/longTail \i.png}
                    \caption{t=\i}
                \end{subfigure}\quad
            }
            \caption{3 Community test series. This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the long tail system.}
            \label{longtail series}
        \end{figure}
        In fig \autoref{longtail series} we see the true embedding of the target node jump from one arm to the other at each timestep. It is clear that neither the the symbolic regression model nor the neural network model capture this movement, but the symbolic regression model does not move away from the data as quickly as the neural network model does.

@@

    \begin{subsection}{Three Community (Please Review)}
        \begin{figure}
            \foreach \i in {1,...,15} {%
                \begin{subfigure}[p]{0.3\textwidth}
                    \includegraphics[width=\linewidth]{/home/stirling/thesis/Conference Submission/Plots/Test Only/3community/3community \i.png}
                    \caption{t=\i}
                \end{subfigure}\quad
            }
            \caption{Long tail test series. This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the 3 community system.}
            \label{3community series}
        \end{figure}
        In fig \autoref{3community series} we again, as the edges between the community with the fewest edges are removed, we see the target node move away from it in the embedding and towards the other two clusters of points (communities).

>>>>

\begin{section}{Results and Discussion}
    For each of theses systems, we took embedded the temporal network in two dimensions at each time step. The temporal embeddings were then divided into a training set of 20 and a testing set of 15. The output of the trained neural networks was then used to train a symbolic regression model that could use a simple set of addition, subtraction, division, and multiplication. \\
    In fig \autoref{2community series}, \autoref{longtail series},\autoref{3community series} the green points are the embedded coordinates of the node in each of the communities. Each cluster is one separate community. The orange point is the true coordinate of the embedded target node at each time step. The blue point is our model prediction from the true target node at the first time step. As the time progresses, we see the true node move from one community cluster to the other. This is expected from the embedding; the target node starts as very similar to the first community (as it has many connections with nodes in that community) and as time progresses, it gradually becomes less and less similar to the first community and more similar to the second (as the edges between the target node and the first community are replaced with edges to the second community). As such, we see the target node move towards the second community.
    \begin{subsection}{2 Community}
        \begin{figure}
            \foreach \i in {1,...,15} {%
                \begin{subfigure}[p]{0.3\textwidth}
                    \includegraphics[width=\linewidth]{./Plots/Test Only/2communities/2communities \i.png}
                    \caption{t=\i}
                \end{subfigure}\quad
            }
            \caption{2 Community test series. This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the two community system.}
            \label{2community series}
        \end{figure}

@@

    \begin{subsection}{Long Tail}
        \begin{figure} 
            \foreach \i in {1,...,15} {%
                \begin{subfigure}[p]{0.3\textwidth}
                    \includegraphics[width=\linewidth]{./Plots/Test Only/longTail/longTail \i.png}
                    \caption{t=\i}
                \end{subfigure}\quad
            }
            \caption{3 Community test series. This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the long tail system.}
            \label{longtail series}
        \end{figure}
        In fig \autoref{longtail series} we see the true embedding of the target node jump from one arm to the other at each timestep. It is clear that neither the the symbolic regression model nor the neural network model capture this movement, but the symbolic regression model does not move away from the data as quickly as the neural network model does.

@@

    \begin{subsection}{Three Community (Please Review)}
        \begin{figure}
            \foreach \i in {1,...,15} {%
                \begin{subfigure}[p]{0.3\textwidth}
                    \includegraphics[width=\linewidth]{./Plots/Test Only/3community/3community \i.png}
                    \caption{t=\i}
                \end{subfigure}\quad
            }
            \caption{Long tail test series. This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the 3 community system.}
            \label{3community series}
        \end{figure}
        In fig \autoref{3community series} we again, as the edges between the community with the fewest edges are removed, we see the target node move away from it in the embedding and towards the other two clusters of points (communities).
